Barneby Lives usage example

### 2023-05-12 scripts/crop2boundary.Rmd
cleaning places

@@

>>>>

sf::st_read('../geodata/places/places.shp', quiet = T) %>% 
  mutate(
    fetr_nm = str_remove(fetr_nm, ' Census Designated Place' ),
    fetr_nm = str_remove(fetr_nm, 'Township of '), 
    fetr_nm = str_remove(fetr_nm, ' \\(historical\\)'),
    fetr_nm = str_remove(fetr_nm, 'Village of '),
    fetr_nm = str_remove(fetr_nm, 'Town of '), 
    fetr_nm = str_remove(fetr_nm, 'City of ')
    ) %>% 
  filter(!str_detect(fetr_nm,
                     'Election Precinct| County|Ditch|Unorganized Territory|Canal|Lateral|Division|
                     River Division|Drain Number|Waste Pond|Commissioner District|Lake Superior|Lake Michigan')) %>% 
  st_write(., '../geodata/places/places.shp', quiet = T, append = F)

@@

' Lake', ' lk.'
' Canyon', ' cnyn.'
' Campground', ' cmpgrnd.'
' Creek', ' crk.'
' River', ' rvr.'
' Reservoir', ' rsvr.'
' Fork', ' fk.'
' Number', ' #'
' Mountain', ' mtn.'
' Mountains', ' mtns.'
' Meadow', ' mdw.'
' Meadows' , ' mdws.'
' Point', ' pt.'

### 2023-05-12 scripts/project_template.Rmd
cleaning places

```{r}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 50), seq(1:50)),
  day = c(sample(1:31, size = 50, replace = T)),
  month = c(sample(5:10, size = 50, replace = T)),
  year = 2023,
  x = runif(50, min = -120, max = -85), 
  y = runif(50, min = 35, max = 48)
) %>% sf::st_as_sf(coords = c(x = 'x', y = 'y'), crs = 4326)

@@

political <- sf::st_read('../geodata/political/political.shp', quiet = T)
allotment <- sf::st_read('../geodata/allotments/allotments.shp', quiet = T)
plss <- sf::st_read('../geodata/plss/plss.shp', quiet = T)
ownership <- sf::st_read('../geodata/pad/pad.shp', quiet = T)

x <- sf::st_join(x, political) 
x <- sf::st_join(x, allotment) 
x <- sf::st_join(x, ownership)

x_plss <- sf::st_transform(x, sf::st_crs(plss))
x_plss <- sf::st_join(x_plss, plss)

x_vars <- dplyr::left_join(x, x_plss)

@@

head(dummy_ownership)

>>>>

```{r}
dummy_pts <- data.frame(
  collectionNo = paste0(rep('RCB', 500), seq(1:500)),
  day = c(sample(1:31, size = 500, replace = T)),
  month = c(sample(5:10, size = 500, replace = T)),
  year = 2023,
  x = runif(500, min = -120, max = -85), 
  y = runif(500, min = 35, max = 48)
) %>% sf::st_as_sf(coords = c(x = 'x', y = 'y'), crs = 4326)

@@

@@
